---
title: "Spain_study"
author: "arti"
date: "1/9/2020"
output: html_document
---
#This project is statistical analysis for a 3X1 facotrial experiment. Experiment contain four scenarios for each of three conditions.
# The conditions involve AI, Human and Human aided by AI. each of these are summy coded # to run the regression model.
# TRUST, CREDEBILITY, QUALITY, AND FAIRNESS are the dependent variables as perceived by #participants. conditions is independent variable.

# Step-1: pre-process data to remove participants who failed the required checks.
# Step-2: Plot the over all projection for 3 issues in each of three conditions
# Step-3: run ANOVA
# Step-4: run multiple regression models.
# Step-5: plotting interaction

```{r}
require(ggplot2)
require(dplyr)
require(ggpubr)
```
```{r}
ex.data=read.csv("C:\\Users\\arti\\Documents\\AI-perception\\data\\AI Experiment ES_January 8 final.xlsb.csv")
dat_com = ex.data %>% filter((SOCIAL_1!=1 | SOCIAL_2!=1 | SOCIAL_3 !=1 | SOCIAL_4!=1 ) & CHECK==2)
dat_com$Duration..in.seconds. <- as.numeric(dat_com$Duration..in.seconds.)
class(dat_com$Duration..in.seconds.)
dat_com_str<- dat_com
median(as.numeric(ex.data$Duration..in.seconds.))
quantile(ex.data$Duration..in.seconds., na.rm = T)

#excluding-speeders
dat_com_str_sp<-dat_com_str %>%
  filter(Duration..in.seconds. > 295.20)
nrow(dat_com_str_sp)

#### excluding duplicates
final_data_Spain <- dat_com_str_sp %>% distinct(pid, .keep_all = T)
nrow(final_data_Spain)
N<-nrow(final_data_Spain)

```
```{r}

final_data_Spain$AI.dummy <- ifelse(final_data_Spain$condition %in% c(2,3),0,1)
final_data_Spain$Human.dummy <- ifelse(final_data_Spain$condition %in% c(1,3),0,1)
final_data_Spain$AI_Human.dummy <- ifelse(final_data_Spain$condition %in% c(1,2),0,1)

final_data_Spain$sp1mean.trust <- (final_data_Spain$TRUST+final_data_Spain$CIVIL_TRUST+ final_data_Spain$FACTS_TRUST+ final_data_Spain$DEC_TRUST)/4
final_data_Spain$sp1mean.fair <- (final_data_Spain$FAIR+final_data_Spain$CIVIL_FAIR+ final_data_Spain$FACTS_FAIR+ final_data_Spain$DEC_FAIR)/4
final_data_Spain$sp1mean.biased <- (final_data_Spain$BIASED+final_data_Spain$CIVIL_BIASED+ final_data_Spain$FACTS_BIASED+ final_data_Spain$DEC_BIASED)/4
final_data_Spain$sp1mean.agree <- (final_data_Spain$AGREE+final_data_Spain$CIVIL_AGREE+ final_data_Spain$FACTS_AGREE+ final_data_Spain$DEC_AGREE)/4
```



```{r randomization check}
#summary(aov(scale(condition)~scale(RACE), data = subset(final_data, !is.na(RACE)) ), na.rm=T)
summary(aov(scale(condition)~scale(INCOME) , data = subset(final_data_Spain,!is.na(INCOME))), na.rm=T)
#summary(aov(scale(condition)~scale(COMUNIDAD_AUT) , data = subset(final_data_Spain,!is.na(COMUNIDAD_AUT))), na.rm=T)
summary(aov(scale(condition)~scale(GENDER) , data = subset(final_data_Spain,!is.na(GENDER))), na.rm=T)
summary(aov(scale(condition)~scale(EDU), data = subset(final_data_Spain, !is.na(EDU))), na.rm=T)
summary(aov(scale(condition)~scale(AGE_CAT), data = subset(final_data_Spain, !is.na(AGE_CAT))), na.rm=T)
#summary(aov(scale(condition)~scale(PARTY7), data = subset(final_data, !is.na(PARTY7))), na.rm=T)
summary(aov(scale(condition)~scale(IDEO_1), data = subset(final_data_Spain, !is.na(IDEO_1))), na.rm=T)
summary(aov(scale(condition)~scale(FOLLOW), data = subset(final_data_Spain, !is.na(FOLLOW))), na.rm=T)
summary(aov(scale(condition)~scale(INCOME), data = subset(final_data_Spain, !is.na(FOLLOW))), na.rm=T)
#summary(aov(scale(condition)~scale(AI_2), data = subset(final_data, !is.na(AI_2))), na.rm=T)


```

```{r }
#manipulating data for plotting scenariowise projections
s1_1<- final_data_Spain %>% select("TRUST","FAIR","BIASED","AGREE","condition", "AI.dummy","Human.dummy","AI_Human.dummy","EDU")
s1_1[ncol(s1_1)+1]<- rep(1, nrow(s1_1))
s1_2<- final_data_Spain %>% select("CIVIL_TRUST","CIVIL_FAIR","CIVIL_BIASED","CIVIL_AGREE","condition", "AI.dummy","Human.dummy","AI_Human.dummy","EDU")
s1_2[ncol(s1_2)+1]<- rep(2, nrow(s1_2))
s1_3<- final_data_Spain %>% select("FACTS_TRUST","FACTS_FAIR","FACTS_BIASED","FACTS_AGREE","condition", "AI.dummy","Human.dummy","AI_Human.dummy","EDU")
s1_3[ncol(s1_3)+1]<- rep(3, nrow(s1_3))
s1_4<- final_data_Spain %>% select("DEC_TRUST","DEC_FAIR","DEC_BIASED","DEC_AGREE","condition", "AI.dummy","Human.dummy","AI_Human.dummy","EDU")
s1_4[ncol(s1_4)+1]<- rep(4, nrow(s1_4))

colnames(s1_2)[which(names(s1_2) == "CIVIL_TRUST")] <- "TRUST"
colnames(s1_3)[which(names(s1_3) == "FACTS_TRUST")] <- "TRUST"
colnames(s1_4)[which(names(s1_4) == "DEC_TRUST")] <- "TRUST"
colnames(s1_2)[which(names(s1_2) == "CIVIL_FAIR")] <- "FAIR"
colnames(s1_3)[which(names(s1_3) == "FACTS_FAIR")] <- "FAIR"
colnames(s1_4)[which(names(s1_4) == "DEC_FAIR")] <- "FAIR"
colnames(s1_2)[which(names(s1_2) == "CIVIL_AGREE")] <- "AGREE"
colnames(s1_3)[which(names(s1_3) == "FACTS_AGREE")] <- "AGREE"
colnames(s1_4)[which(names(s1_4) == "DEC_AGREE")] <- "AGREE"
colnames(s1_2)[which(names(s1_2) == "CIVIL_BIASED")] <- "BIASED"
colnames(s1_3)[which(names(s1_3) == "FACTS_BIASED")] <- "BIASED"
colnames(s1_4)[which(names(s1_4) == "DEC_BIASED")] <- "BIASED"

df1<- rbind(s1_1,s1_2,s1_3,s1_4)
colnames(df1)[which(names(df1) == "V10")] <- "scenario"
```



```{r}
################################################### Overall ######################################################
summary(aov((sp1mean.trust) ~ (condition), data = final_data_Spain), na.rm=T)
summary(aov((sp1mean.fair) ~ (condition) , data = final_data_Spain), na.rm=T)
summary(aov((sp1mean.biased) ~ (condition) , data = final_data_Spain), na.rm=T)
summary(aov((sp1mean.agree) ~ (condition), data = final_data_Spain), na.rm=T)

summary(lm((sp1mean.trust) ~ (AI.dummy) + (AI_Human.dummy) , data = final_data_Spain), na.rm=T)
summary(lm((sp1mean.fair) ~ (AI.dummy) + (AI_Human.dummy) , data = final_data_Spain), na.rm=T)
summary(lm((sp1mean.biased) ~ (AI.dummy) + (AI_Human.dummy) , data = final_data_Spain), na.rm=T)
summary(lm((sp1mean.agree) ~ (AI.dummy) + (AI_Human.dummy), data = final_data_Spain), na.rm=T)

summary(lm((sp1mean.trust) ~ (Human.dummy) + (AI_Human.dummy) , data = final_data_Spain), na.rm=T)
summary(lm((sp1mean.fair) ~ (Human.dummy) + (AI_Human.dummy) , data = final_data_Spain), na.rm=T)
summary(lm((sp1mean.biased) ~ (Human.dummy) + (AI_Human.dummy) , data = final_data_Spain), na.rm=T)
summary(lm((sp1mean.agree) ~ (Human.dummy) + (AI_Human.dummy), data = final_data_Spain), na.rm=T)

################################################### Scenari-1 ######################################################
summary(aov((TRUST) ~ (condition), data = final_data_Spain), na.rm=T)
summary(aov((FAIR) ~ (condition) , data = final_data_Spain), na.rm=T)
summary(aov((BIASED) ~ (condition) , data = final_data_Spain), na.rm=T)
summary(aov((AGREE) ~ (condition), data = final_data_Spain), na.rm=T)

summary(lm((TRUST) ~ (AI.dummy) + (AI_Human.dummy) , data = final_data_Spain), na.rm=T)
summary(lm((FAIR) ~ (AI.dummy) + (AI_Human.dummy) , data = final_data_Spain), na.rm=T)
summary(lm((BIASED) ~ (AI.dummy) + (AI_Human.dummy) , data = final_data_Spain), na.rm=T)
summary(lm((AGREE) ~ (AI.dummy) + (AI_Human.dummy), data = final_data_Spain), na.rm=T)

summary(lm((TRUST) ~ (Human.dummy) + (AI_Human.dummy) , data = final_data_Spain), na.rm=T)
summary(lm((FAIR) ~ (Human.dummy) + (AI_Human.dummy) , data = final_data_Spain), na.rm=T)
summary(lm((BIASED) ~ (Human.dummy) + (AI_Human.dummy) , data = final_data_Spain), na.rm=T)
summary(lm((AGREE) ~ (Human.dummy) + (AI_Human.dummy), data = final_data_Spain), na.rm=T)

################################################### Scenari-2 ######################################################
summary(aov((CIVIL_TRUST) ~ (condition), data = final_data_Spain), na.rm=T)
summary(aov((CIVIL_FAIR) ~ (condition) , data = final_data_Spain), na.rm=T)
summary(aov((CIVIL_BIASED) ~ (condition) , data = final_data_Spain), na.rm=T)
summary(aov((CIVIL_AGREE) ~ (condition), data = final_data_Spain), na.rm=T)

summary(lm((CIVIL_TRUST) ~ (AI.dummy) + (AI_Human.dummy), data = final_data_Spain), na.rm=T)
summary(lm((CIVIL_FAIR) ~ (AI.dummy) + (AI_Human.dummy), data = final_data_Spain), na.rm=T)
summary(lm((CIVIL_BIASED) ~ (AI.dummy) + (AI_Human.dummy) , data = final_data_Spain), na.rm=T)
summary(lm((CIVIL_AGREE) ~ (AI.dummy) + (AI_Human.dummy), data = final_data_Spain), na.rm=T)

summary(lm((CIVIL_TRUST) ~ (Human.dummy) + (AI_Human.dummy), data = final_data_Spain), na.rm=T)
summary(lm((CIVIL_FAIR) ~ (Human.dummy) + (AI_Human.dummy) , data =final_data_Spain), na.rm=T)
summary(lm((CIVIL_BIASED) ~ (Human.dummy) + (AI_Human.dummy), data = final_data_Spain), na.rm=T)
summary(lm((CIVIL_AGREE) ~ (Human.dummy) + (AI_Human.dummy), data = final_data_Spain), na.rm=T)

################################################### Scenario-3 ######################################################
summary(aov((FACTS_TRUST) ~ (condition), data = final_data_Spain), na.rm=T)
summary(aov((FACTS_FAIR) ~ (condition) , data = final_data_Spain), na.rm=T)
summary(aov((FACTS_BIASED) ~ (condition) , data = final_data_Spain), na.rm=T)
summary(aov((FACTS_AGREE) ~ (condition), data = final_data_Spain), na.rm=T)

summary(lm((FACTS_TRUST) ~ (AI.dummy) + (AI_Human.dummy) , data = final_data_Spain), na.rm=T)
summary(lm((FACTS_FAIR) ~ (AI.dummy) + (AI_Human.dummy) , data = final_data_Spain), na.rm=T)
summary(lm((FACTS_BIASED) ~ (AI.dummy) + (AI_Human.dummy) , data = final_data_Spain), na.rm=T)
summary(lm((FACTS_AGREE) ~ (AI.dummy) + (AI_Human.dummy), data = final_data_Spain), na.rm=T)

summary(lm((FACTS_TRUST) ~ (Human.dummy) + (AI_Human.dummy) , data = final_data_Spain), na.rm=T)
summary(lm((FACTS_FAIR) ~ (Human.dummy) + (AI_Human.dummy) , data = final_data_Spain), na.rm=T)
summary(lm((FACTS_BIASED) ~ (Human.dummy) + (AI_Human.dummy) , data = final_data_Spain), na.rm=T)
summary(lm((FACTS_AGREE) ~ (Human.dummy) + (AI_Human.dummy), data = final_data_Spain), na.rm=T)

################################################### Scenari-4 ######################################################
summary(aov((DEC_TRUST) ~ (condition), data = final_data_Spain), na.rm=T)
summary(aov((DEC_FAIR) ~ (condition) , data = final_data_Spain), na.rm=T)
summary(aov((DEC_BIASED) ~ (condition) , data = final_data_Spain), na.rm=T)
summary(aov((DEC_AGREE) ~ (condition), data = final_data_Spain), na.rm=T)

summary(lm((DEC_TRUST) ~ (AI.dummy) + (AI_Human.dummy) , data = final_data_Spain), na.rm=T)
summary(lm((DEC_FAIR) ~ (AI.dummy) + (AI_Human.dummy) , data = final_data_Spain), na.rm=T)
summary(lm((DEC_BIASED) ~ (AI.dummy) + (AI_Human.dummy) , data = final_data_Spain), na.rm=T)
summary(lm((DEC_AGREE) ~ (AI.dummy) + (AI_Human.dummy), data = final_data_Spain), na.rm=T)

summary(lm((DEC_TRUST) ~ (Human.dummy) + (AI_Human.dummy) , data = final_data_Spain), na.rm=T)
summary(lm((DEC_FAIR) ~ (Human.dummy) + (AI_Human.dummy) , data = final_data_Spain), na.rm=T)
summary(lm((DEC_BIASED) ~ (Human.dummy) + (AI_Human.dummy) , data = final_data_Spain), na.rm=T)
summary(lm((DEC_AGREE) ~ (Human.dummy) + (AI_Human.dummy), data = final_data_Spain), na.rm=T)
```



```{r Plots}


study1.data1 <- df1 %>% group_by(scenario, condition) %>% summarise(
  "mean.quality" = mean(as.numeric(TRUST),na.rm=TRUE),
  "sd.quality" = sd(as.numeric(TRUST), na.rm = TRUE),
  "N" = length(TRUST),
) %>% mutate("se.quality" = sd.quality/ sqrt(N))
s1_g1<-ggplot(data = study1.data1, aes(x = as.factor(scenario), y = mean.quality, fill = as.factor(condition))) + 
  geom_bar(stat = "identity",
           color = "orange", position = position_dodge()) + 
  scale_fill_manual(values = c(blues9, "blue", "naviblue"),
                    "Conditions") + 
  geom_errorbar(width = .5, 
                aes(ymin = mean.quality - se.quality, 
                    ymax = mean.quality + se.quality), position = position_dodge(.9))  + 
  labs(x = "Scenarios",
       y = "Percieved Trust",
       title = "Perception of Trust by agents") + 
  theme_classic()

study1.data2 <- df1 %>% group_by(scenario, condition) %>% summarise(
  "mean.biased" = mean(as.numeric(BIASED), na.rm = TRUE),
  "sd.biased" = sd(as.numeric(BIASED), na.rm = TRUE),
  "N" = length(BIASED),
) %>% mutate("se.biased" = sd.biased/ sqrt(N))
s1_g2<-ggplot(data = study1.data2, aes(x = as.factor(scenario), y = mean.biased, fill = as.factor(condition))) + 
  geom_bar(stat = "identity",
           color = "orange", position = position_dodge()) + 
  scale_fill_manual(values = c(blues9, "blue", "naviblue"),
                    "Conditions") + 
  geom_errorbar(width = .5, 
                aes(ymin = mean.biased - se.biased, 
                    ymax = mean.biased + se.biased), position = position_dodge(.9))  + 
  labs(x = "Scenarios",
       y = "Percieved Biasness",
       title = "Perception of Biasness by agents") + 
  theme_classic()



study1.data3 <- df1 %>% group_by(scenario, condition) %>% summarise(
  "mean.cred" = mean(as.numeric(FAIR), na.rm = TRUE),
  "sd.cred" = sd(as.numeric(FAIR), na.rm = TRUE),
  "N" = length(FAIR),
) %>% mutate("se.cred" = sd.cred/ sqrt(N))
s1_g3<-ggplot(data = study1.data3, aes(x = as.factor(scenario), y = mean.cred, fill = as.factor(condition))) + 
  geom_bar(stat = "identity",
           color = "orange", position = position_dodge()) + 
  scale_fill_manual(values = c(blues9, "blue", "naviblue"),
                    "Conditions") + 
  geom_errorbar(width = .5, 
                aes(ymin = mean.cred - se.cred, 
                    ymax = mean.cred + se.cred), position = position_dodge(.9))  + 
  labs(x = "Scenarios",
       y = "Percieved fairness in decision",
       title = "Perception of fairness by agents") + 
  theme_classic()

study1.data4 <- df1 %>% group_by(scenario,condition) %>% summarise(
  "mean.agree" = mean(as.numeric(AGREE), na.rm = TRUE),
  "sd.agree" = sd(as.numeric(AGREE), na.rm = TRUE),
  "N" = length(AGREE),
) %>% mutate("se.agree" = sd.agree/ sqrt(N))
s1_g4<-ggplot(data = study1.data4, aes(x = as.factor(scenario), y = mean.agree, fill = as.factor(condition))) + 
  geom_bar(stat = "identity",
           color = "orange", position = position_dodge()) + 
  scale_fill_manual(values = c(blues9, "blue", "naviblue"),
                    "Conditions") + 
  geom_errorbar(width = .5, 
                aes(ymin = mean.agree - se.agree, 
                    ymax = mean.agree + se.agree), position = position_dodge(.9))  + 
  labs(x = "Scenarios",
       y = "Percieved Agreeability",
       title = "Perception of Agreeability by conditions") + 
  theme_classic()

ggarrange(s1_g1,s1_g2,s1_g3,s1_g4)
```




```{r overall results}
study2.data1 <- df1 %>% group_by(condition) %>% summarise(
  "mean.trust" = mean(as.numeric(TRUST),na.rm=TRUE),
  "sd.trust" = sd(as.numeric(TRUST), na.rm = TRUE),
  "N" = length(TRUST),
) %>% mutate("se.trust" = sd.trust/ sqrt(N))
s2_g1<-ggplot(data = study2.data1, aes(x = as.factor(condition), y = mean.trust, fill = as.factor(condition))) + 
  geom_bar(stat = "identity",
           color = "orange", position = position_dodge()) + 
  scale_fill_manual(values = c(blues9, "blue", "naviblue"),
                    "Conditions") + 
  geom_errorbar(width = .5, 
                aes(ymin = mean.trust - se.trust, 
                    ymax = mean.trust - se.trust), position = position_dodge(.9))  + 
  labs(x = "conditions",
       y = "Percieved Trust",
       title = "Perception of Trust by agents") + 
  theme_classic()

study2.data2 <- df1 %>% group_by(condition) %>% summarise(
  "mean.biased" = mean(as.numeric(BIASED), na.rm = TRUE),
  "sd.biased" = sd(as.numeric(BIASED), na.rm = TRUE),
  "N" = length(BIASED),
) %>% mutate("se.biased" = sd.biased/ sqrt(N))
s2_g2<-ggplot(data = study2.data2, aes(x = as.factor(condition), y = mean.biased, fill = as.factor(condition))) + 
  geom_bar(stat = "identity",
           color = "orange", position = position_dodge()) + 
  scale_fill_manual(values = c(blues9, "blue", "naviblue"),
                    "Conditions") + 
  geom_errorbar(width = .5, 
                aes(ymin = mean.biased - se.biased, 
                    ymax = mean.biased + se.biased), position = position_dodge(.9))  + 
  labs(x = "conditions",
       y = "Percieved Biasness",
       title = "Perception of Biasness by agents") + 
  theme_classic()



study2.data3 <- df1 %>% group_by(condition) %>% summarise(
  "mean.fair" = mean(as.numeric(FAIR), na.rm = TRUE),
  "sd.fair" = sd(as.numeric(FAIR), na.rm = TRUE),
  "N" = length(FAIR),
) %>% mutate("se.fair" = sd.fair/ sqrt(N))
s2_g3<-ggplot(data = study2.data3, aes(x = as.factor(condition), y = mean.fair, fill = as.factor(condition))) + 
  geom_bar(stat = "identity",
           color = "orange", position = position_dodge()) + 
  scale_fill_manual(values = c(blues9, "blue", "naviblue"),
                    "Conditions") + 
  geom_errorbar(width = .5, 
                aes(ymin = mean.fair - se.fair, 
                    ymax = mean.fair - se.fair), position = position_dodge(.9))  + 
  labs(x = "Conditions",
       y = "Percieved Fairness in decision",
       title = "Perception of Fairness by agents") + 
  theme_classic()

study2.data4 <- df1 %>% group_by(condition) %>% summarise(
  "mean.agree" = mean(as.numeric(AGREE), na.rm = TRUE),
  "sd.agree" = sd(as.numeric(AGREE), na.rm = TRUE),
  "N" = length(AGREE),
) %>% mutate("se.agree" = sd.agree/ sqrt(N))
s2_g4<-ggplot(data = study2.data4, aes(x = as.factor(condition), y = mean.agree, fill = as.factor(condition))) + 
  geom_bar(stat = "identity",
           color = "orange", position = position_dodge()) + 
  scale_fill_manual(values = c(blues9, "blue", "naviblue"),
                    "Conditions") + 
  geom_errorbar(width = .5, 
                aes(ymin = mean.agree - se.agree, 
                    ymax = mean.agree + se.agree), position = position_dodge(.9))  + 
  labs(x = "Conditions",
       y = "Percieved Agreeability",
       title = "Perception of Agreeability by conditions") + 
  theme_classic()

ggarrange(s2_g1,s2_g2,s2_g3,s2_g4)
```

```{r Plots for overall results for study1}
Spainstudy1.d1 <- final_data_Spain %>% group_by(condition) %>% summarise(
  "mean_trust" = mean(as.numeric(sp1mean.trust), na.rm = TRUE),
  "sd.trust" = sd(as.numeric(sp1mean.trust), na.rm = TRUE),
  "N" = length(sp1mean.trust),
) %>% mutate("se.trust" = sd.trust/ sqrt(N))
Spain.s1g1<-ggplot(data = Spainstudy1.d1, aes(x = as.factor(condition), y = mean_trust, fill = as.factor(condition))) + 
  geom_bar(stat = "identity",
           color = "orange", position = position_dodge()) + 
  scale_fill_manual(values = c(blues9, "blue", "naviblue"),
                    "Conditions") + 
  geom_errorbar(width = .5, 
                aes(ymin = mean_trust - se.trust, 
                    ymax = mean_trust + se.trust), position = position_dodge(.9))  + 
  labs(x = "conditions",
       y = "Percieved Trust",
       title = "Perception of Trust by agents") + 
  theme_classic()

Spainstudy1.d2 <- final_data_Spain %>% group_by(condition) %>% summarise(
  "mean_biased" = mean(as.numeric(sp1mean.biased), na.rm = TRUE),
  "sd.biased" = sd(as.numeric(sp1mean.biased), na.rm = TRUE),
  "N" = length(sp1mean.biased),
) %>% mutate("se.biased" = sd.biased/ sqrt(N))
Spain.s1g2<-ggplot(data = Spainstudy1.d2, aes(x = as.factor(condition), y = mean_biased, fill = as.factor(condition))) + 
  geom_bar(stat = "identity",
           color = "orange", position = position_dodge()) + 
  scale_fill_manual(values = c(blues9, "blue", "naviblue"),
                    "Conditions") + 
  geom_errorbar(width = .5, 
                aes(ymin = mean_biased - se.biased, 
                    ymax = mean_biased + se.biased), position = position_dodge(.9))  + 
  labs(x = "conditions",
       y = "Percieved Biasness",
       title = "Perception of Biasness by agents") + 
  theme_classic()



Spainstudy1.d3 <- final_data_Spain %>% group_by(condition) %>% summarise(
  "mean_fair" = mean(as.numeric(sp1mean.fair), na.rm = TRUE),
  "sd.fair" = sd(as.numeric(sp1mean.fair), na.rm = TRUE),
  "N" = length(sp1mean.fair),
) %>% mutate("se.fair" = sd.fair/ sqrt(N))
Spain.s1g3<-ggplot(data = Spainstudy1.d3, aes(x = as.factor(condition), y = mean_fair, fill = as.factor(condition))) + 
  geom_bar(stat = "identity",
           color = "orange", position = position_dodge()) + 
  scale_fill_manual(values = c(blues9, "blue", "naviblue"),
                    "Conditions") + 
  geom_errorbar(width = .5, 
                aes(ymin = mean_fair - se.fair, 
                    ymax = mean_fair + se.fair), position = position_dodge(.9))  + 
  labs(x = "conditions",
       y = "Percieved Fairness",
       title = "Perception of Fairness by agents") + 
  theme_classic()

Spainstudy1.d4 <- final_data_Spain %>% group_by(condition) %>% summarise(
  "mean_agree" = mean(as.numeric(sp1mean.agree), na.rm = TRUE),
  "sd.agree" = sd(as.numeric(sp1mean.agree), na.rm = TRUE),
  "N" = length(sp1mean.agree),
) %>% mutate("se.agree" = sd.agree/ sqrt(N))
Spain.s1g4<-ggplot(data = Spainstudy1.d4, aes(x = as.factor(condition), y = mean_agree, fill = as.factor(condition))) + 
  geom_bar(stat = "identity",
           color = "orange", position = position_dodge()) + 
  scale_fill_manual(values = c(blues9, "blue", "naviblue"),
                    "Conditions") + 
  geom_errorbar(width = .5, 
                aes(ymin = mean_agree - se.agree, 
                    ymax = mean_agree + se.agree), position = position_dodge(.9))  + 
  labs(x = "Conditions",
       y = "Percieved Agreeability",
       title = "Perception of Agreeability by conditions") + 
  theme_classic()

ggarrange(Spain.s1g1,Spain.s1g2,Spain.s1g3,Spain.s1g4)
ggsave("Spain study1 combined plots.jpeg")
```

```{r plots for combined results for study2}
Spainstudy2.d1 <- final_data_Spain %>% group_by(condition) %>% summarise(
  "mean_cred" = mean(as.numeric(sp2mean.cred), na.rm = TRUE),
  "sd.cred" = sd(as.numeric(sp2mean.cred), na.rm = TRUE),
  "N" = length(sp2mean.cred),
) %>% mutate("se.cred" = sd.cred/ sqrt(N))
Spain.s2g1<-ggplot(data = Spainstudy2.d1, aes(x = as.factor(condition), y = mean_cred, fill = as.factor(condition))) + 
  geom_bar(stat = "identity",
           color = "orange", position = position_dodge()) + 
  scale_fill_manual(values = c(blues9, "blue", "naviblue"),
                    "Conditions") + 
  geom_errorbar(width = .5, 
                aes(ymin = mean_cred - se.cred, 
                    ymax = mean_cred + se.cred), position = position_dodge(.9))  + 
  annotate("text", label = "Stats to be Displayed")+
  labs(x = "conditions",
       y = "Percieved Trust",
       title = "Perception of Trust by agents") + 
  theme_classic()

Spainstudy2.d2 <- final_data_Spain %>% group_by(condition) %>% summarise(
  "mean_biased" = mean(as.numeric(sp2mean.biased), na.rm = TRUE),
  "sd.biased" = sd(as.numeric(sp2mean.biased), na.rm = TRUE),
  "N" = length(sp2mean.biased),
) %>% mutate("se.biased" = sd.biased/ sqrt(N))
Spain.s2g2<-ggplot(data = Spainstudy2.d2, aes(x = as.factor(condition), y = mean_biased, fill = as.factor(condition))) + 
  geom_bar(stat = "identity",
           color = "orange", position = position_dodge()) + 
  scale_fill_manual(values = c(blues9, "blue", "naviblue"),
                    "Conditions") + 
  geom_errorbar(width = .5, 
                aes(ymin = mean_biased - se.biased, 
                    ymax = mean_biased + se.biased), position = position_dodge(.9))  + 
  labs(x = "conditions",
       y = "Percieved Biasness",
       title = "Perception of Biasness by agents") + 
  theme_classic()



Spainstudy2.d3 <- final_data_Spain %>% group_by(condition) %>% summarise(
  "mean_quality" = mean(as.numeric(sp2mean.quality), na.rm = TRUE),
  "sd.quality" = sd(as.numeric(sp2mean.quality), na.rm = TRUE),
  "N" = length(sp2mean.quality),
) %>% mutate("se.quality" = sd.quality/ sqrt(N))
Spain.s2g3<-ggplot(data = Spainstudy2.d3, aes(x = as.factor(condition), y = mean_quality, fill = as.factor(condition))) + 
  geom_bar(stat = "identity",
           color = "orange", position = position_dodge()) + 
  scale_fill_manual(values = c(blues9, "blue", "naviblue"),
                    "Conditions") + 
  geom_errorbar(width = .5, 
                aes(ymin = mean_quality - se.quality, 
                    ymax = mean_quality + se.quality), position = position_dodge(.9))  + 
  labs(x = "conditions",
       y = "Percieved Quality",
       title = "Perception of Quality by agents") + 
  theme_classic()

Spainstudy2.d4 <- final_data_Spain %>% group_by(condition) %>% summarise(
  "mean_agree" = mean(as.numeric(sp1mean.agree), na.rm = TRUE),
  "sd.agree" = sd(as.numeric(sp1mean.agree), na.rm = TRUE),
  "N" = length(sp1mean.agree),
) %>% mutate("se.agree" = sd.agree/ sqrt(N))
Spain.s2g4<-ggplot(data = Spainstudy2.d4, aes(x = as.factor(condition), y = mean_agree, fill = as.factor(condition))) + 
  geom_bar(stat = "identity",
           color = "orange", position = position_dodge()) + 
  scale_fill_manual(values = c(blues9, "blue", "naviblue"),
                    "Conditions") + 
  geom_errorbar(width = .5, 
                aes(ymin = mean_agree - se.agree, 
                    ymax = mean_agree + se.agree), position = position_dodge(.9))  + 
  labs(x = "Conditions",
       y = "Percieved Agreeability",
       title = "Perception of Agreeability by conditions") + 
  theme_classic()

ggarrange(Spain.s2g1,Spain.s2g2,Spain.s2g3, Spain.s2g4)
ggsave("Spain study2 combined plots.jpeg")
```




